---
title: "R Notebook"
output:
  html_notebook: default
  pdf_document: default
---

# 1st Level Header

## 2nd Level Header

### 3rd Level Header

Alternative Style for 1st Level Header
======================================

Alternative Style for 1st Level Header
--------------------------------------

*italic* (or _italic_)
**bold** (or __bold__)
`code`
superscript^2^ and subscript~2~
`Jay`


*   Bulleted list item 1

*   Item 2

    * Item 2a

    * Item 2b

1.  Numbered list item 1

1.  Item 2. The numbers are incremented automatically in the output.
1. Item
1. sdf #숫자하고 점만 입력하면 알아서 오내 개꿀이당
1. 캡션을 달면 정상적이 아닌 경우 표시됨.

First Header  | Second Header | Third Header
------------- | ------------- | 
Content Cell  | Content Cell  | Content Cell
Content Cell  | Content Cell  | Content Cell

1. 자세한 사항은 Chat sheet markdownguide.org에 들어가면 많당.
* 심지어 코드를 넣을수도 있따.
```{r setup}
knitr::opts_chunk$set(echo = FALSE)
```
```{r}
1+3
```
---
bibliography: refs.bib
Separate multiple citations with a `;`:
Blah blah [@Ghosh2003a; @Ghosal2000a].

You can add arbitrary comments inside the square brackets:
Blah blah [see @Ghosal2000a, pp. 33-35; also @Ghosh2003a, ch. 1].

Remove the square brackets to create an in-text citation:
@Ghosh2003a says blah, or @Ghosal2000a [p. 33] says blah.

Add a `-` before the citation to suppress the author's name:
Ghosal et al. says blah [-@Ghosh2003a].
---

### References